A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-09-04 summary.tex
tiny changes

We obtain the Solberg-Hoiland criteria for axisymmetric stability for
strictly isothermal, perfectly-coupled dusty gas.  
We show that {\bf the vertical shear associated with thin dust
 layers, however large it is, cannot lead to axisymmetric
  instabilities}. This is consistent with the fact that only 
\emph{non-axisymmetric} Kelvin-Helmholtz instabilities have been 
observed in numerical simulations in the perfectly-coupled limit. 
\citep{chiang08,barranco09,lee10}. We show that 
sharp radial edges in the dust-to-gas ratio cannot persist in
protoplanetary disks, as these imply a sharp entropy gradient and may
thus destablize the disk.

>>>>

We obtain the Solberg-Hoiland criteria for axisymmetric stability for
strictly isothermal, perfectly-coupled dusty gas.  
We show that the vertical shear associated with thin dust
 layers \emph{cannot} lead to axisymmetric
  instabilities, however large it is.  
This is consistent with the fact that only 
\emph{non-axisymmetric} Kelvin-Helmholtz instabilities have been 
observed in numerical simulations in the perfectly-coupled limit 
\citep{chiang08,barranco09,lee10}. We show that 
sharp radial edges in the dust-to-gas ratio cannot persist in
protoplanetary disks, as these imply a sharp entropy gradient and may
thus destablize the disk.
